---
title: "Competitor Benchmarks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Competitor Benchmarks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This page records optional benchmark results for `RJSONIO` and direct JSON
package competitors. The benchmark scripts are kept in the GitHub repository
under `benchmarks/` and are excluded from CRAN package builds.

The numbers are machine-specific. They are useful for checking relative behavior
on one system, but should be rerun locally before making performance claims.
Smaller elapsed-time and memory values are better.

```{r package-versions, echo = FALSE}
version_file <- "figures/benchmarks/package-versions.csv"
if (file.exists(version_file)) {
  versions <- read.csv(version_file, stringsAsFactors = FALSE)
  knitr::kable(versions, caption = "Packages included in the benchmark run")
}
```

```{r environment, echo = FALSE}
environment_file <- "figures/benchmarks/environment.csv"
if (file.exists(environment_file)) {
  environment <- read.csv(environment_file, stringsAsFactors = FALSE)
  knitr::kable(environment, caption = "Benchmark environment")
}
```

## Benchmark Tasks

The benchmark suite compares supported operations across the direct competitor
set:

- parse JSON from a string;
- parse JSON from a file;
- write JSON from R objects;
- validate JSON syntax;
- round-trip R objects through JSON.

The payloads include a numeric vector, a data frame, and a nested list. Packages
that do not support a given operation are skipped for that operation.

## Summary

The summary heatmap is the main comparison. Each cell reports median elapsed
time as a ratio to `RJSONIO`, followed by the absolute median elapsed time. Blue
cells are faster than `RJSONIO` for the same task and payload; orange cells are
slower. A value of `1.00x` is the `RJSONIO` baseline.

```{r benchmark-summary, echo = FALSE, out.width = "100%"}
summary_plot <- "figures/benchmarks/benchmark-summary.png"
if (file.exists(summary_plot)) {
  knitr::include_graphics(summary_plot)
}
```

## Elapsed Time

These bars show the same median timings in milliseconds. `RJSONIO` bars are
shown in the darker color.

```{r elapsed-time, echo = FALSE, out.width = "100%"}
elapsed_plot <- "figures/benchmarks/elapsed-time.png"
if (file.exists(elapsed_plot)) {
  knitr::include_graphics(elapsed_plot)
}
```

## Memory Allocation

These bars show memory allocated by the measured expression. `RJSONIO` bars are
shown in the darker color.

```{r memory-allocation, echo = FALSE, out.width = "100%"}
memory_plot <- "figures/benchmarks/memory-allocation.png"
if (file.exists(memory_plot)) {
  knitr::include_graphics(memory_plot)
}
```

## Relative Elapsed Time

This chart uses `RJSONIO = 1.00x` for each task and payload. Values below
`1.00x` are faster than `RJSONIO`; values above `1.00x` are slower.

```{r relative-time, echo = FALSE, out.width = "100%"}
relative_plot <- "figures/benchmarks/relative-time.png"
if (file.exists(relative_plot)) {
  knitr::include_graphics(relative_plot)
}
```

## Skipped Operations

```{r skipped-operations, echo = FALSE}
skip_file <- "figures/benchmarks/benchmark-skips.csv"
if (file.exists(skip_file)) {
  skips <- read.csv(skip_file, stringsAsFactors = FALSE)
  if (nrow(skips)) {
    knitr::kable(skips, caption = "Skipped packages or operations")
  }
}
```

## Reproducing

Run the benchmarks from the repository root:

```r
source("benchmarks/run-benchmarks.R")
```

The script writes CSV files to `benchmarks/results/` and plots to
`benchmarks/figures/`. It also copies the current benchmark artifacts used by
this page to `vignettes/figures/benchmarks/`.
